Perceptions and Preferences for Meritocracy Scale (PPM-S)

### 2020-01-09 index.Rmd
update0901-2020

This research builds upon previous studies attempting to develop a comprehensive approach to measuring meritocratic beliefs [@Duru-bellat2012, @Kunovich2007, @Newman2015, @Reynolds2014]. The proposed measurement model is based on two axis of analysis, as depicted in Table 1. The first one distinguishes between different types of "beliefs", using instead the terms perceptions and preferences for meritocracy. Perceptions refers to the extent to which people see meritocracy working in their society, which in terms of measurement relates to the "reasons to get ahead" battery, whereas preferences refer to normative expectations that are usually linked to a "should" expression (e.g. whether hard work should be related to payment). The second axis consider the distinction between meritocratic and non-meritocratic dimensions. This aspect has been usually treated as different ends of a same continuum in part of the previous research, an assumption that requieres empirical scrutiny. These non-meritocratic elements usually refer to the use of personal contacts or family advantages to get ahead in life.

>>>>

This research builds upon previous studies attempting to develop a comprehensive approach to measuring meritocratic beliefs [@Duru-bellat2012; @Kunovich2007; @Newman2015; @Reynolds2014]. The proposed measurement model is based on two axis of analysis, as depicted in Table 1. The first one distinguishes between different types of "beliefs", using instead the terms perceptions and preferences for meritocracy. Perceptions refers to the extent to which people see meritocracy working in their society, which in terms of measurement relates to the "reasons to get ahead" battery, whereas preferences refer to normative expectations that are usually linked to a "should" expression (e.g. whether hard work should be related to payment). The second axis consider the distinction between meritocratic and non-meritocratic dimensions. This aspect has been usually treated as different ends of a same continuum in part of the previous research, an assumption that requieres empirical scrutiny. These non-meritocratic elements usually refer to the use of personal contacts or family advantages to get ahead in life.
